BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-08-26 Paper/BOAST.tex
updated article

@@

It was also important to have our construct like for loops to have a syntax
approaching those commonly found in programming languages. For this we needed a
language which could seamlessly pass a block of code to a function.
Ruby~\cite{matsumoto2002ruby} is one such language. It has deep introspection
capabilities as well.

>>>>

\begin{center}
\begin{figure}
\includegraphics[width=\textwidth]{BOAST_Workflow.pdf}
\caption{Structure and Workflow of the BOAST framework.}
\label{fig:boast_workflow}
\end{figure}
\end{center}

@@

It was also important to have our constructs like \emph{for loops} to have a
syntax approaching those commonly found in programming languages. For this we
needed a language which could seamlessly pass a block of code to a function.
Ruby~\cite{matsumoto2002ruby} is one such language. It has deep introspection
capabilities as well.
